---
title: "Analyses for DIAG-NonParty-Radio"
output: 
  html_notebook:
  code_folding: hide
---

```{r setup, include = FALSE}
# R version 4.2.3
# load packages & set options
library(ggpubr) # ggpubr_0.6.0
library(here) # here_1.0.1
library(rstatix) # rstatix_0.7.2
library(showtext) # showtext_0.9-6
library(tidyverse) # tidyverse_2.0.0
knitr::opts_chunk$set(echo = FALSE)

# Read data
dat <- readRDS(here::here("Processed data/processed-data.rds"))

# Demographics
dems <- dat %>%
  select(subject_id, age, pro_age, gender, pro_gender,
    pro_racial_group, partisan_identity, pro_partisan_identity,
    political_ideology, time_taken, time_on_data_security,
    stand_out, deception, deception_coded, further_comments) %>%
  unique()

# Add custom font for plots
font_add("Nunito",
  regular = "~/Library/Fonts/NunitoSans-Regular.ttf",
  italic = "~/Library/Fonts/NunitoSans-Italic.ttf",
  bold = "~/Library/Fonts/NunitoSans-Bold.ttf",
  bolditalic = "~/Library/Fonts/NunitoSans-BoldItalic.ttf")
showtext_auto()

# Custom functions
formp <- function(p, text = FALSE) {
  ## ---------------------------
  ## Format p values
  ##
  ## This function takes in a number between
  ## zero and one or a formatted p-value and outputs
  ## a formatted p-value. If p-value is already formatted
  ## then applying the function changes the format from
  ## "p = .034" to ".034" and vice versa.
  ##
  ## @p p-value to be formatted
  ## @text adds "p = " or "p < " to output
  ##
  ## @out string with formatted p-value
  ## ---------------------------

  # If already formatted but no "p" then add "p"
  if (grepl("^<.\\d{3}$", p)) {
    out <- gsub("<", "*p* < ", p)
  } else if (grepl("^.\\d{3}$", p)) {
    out <- gsub("^", "*p* = ", p)
  # If already formatted and "p" then remove "p"
  } else if (grepl("^p < .\\d{3}$|^\\*p\\* < .\\d{3}$", p)) {
    out <- gsub("\\*?p\\*? < ", "<", p)
  } else if (grepl("^p = .\\d{3}$|^\\*p\\* = .\\d{3}$", p)) {
    out <- gsub("\\*?p\\*? = ", "", p)
  # If not yet formatted and smaller than .001
  } else if (is.numeric(p) && p < 0.001) {
    if (text) {
      out <- "*p* < .001"
    } else {
      out <- "<.001"
    }
  # If not yet formatted and bigger than .001
  } else if (p >= 0.001) {
    p <- format(round(p, 3), nsmall = 3, scientific = FALSE)
    p <- sub("0.", ".", p)
  if (text) {
    out <- paste("*p* =", p)
  } else {
    out <- p
  }
  }
  return(out)
}
forma <- function(number, dec = NULL, lead_zero = TRUE) { # nolint
  ## ---------------------------
  ## Format values in apa style
  ##
  ## This function takes in a number and outputs
  ## a formatted number. If no decimal is provided, then
  ## it uses a heuristic to round the number. If lead_zero
  ## is set to FALSE, then the lead zero of the number is
  ## removed (useful for p-values or eta squared).
  ##
  ## @number input number
  ## @dec optional number of decimals
  ## @lead_zero keep leading zero
  ##
  ## @out formatted number
  ## ---------------------------

  # If dec is logical, interpret as lead_zero
  if (is.logical(dec)) {
    lead_zero <- dec
    dec <- NULL
  }
  # If no decimal is specified, use heuristic
  if (!is.null(dec)) {
  } else if (abs(number) >= 100) {
    dec <- 0
  } else if (abs(number) >= 10 && number < 100) {
    dec <- 1
  } else if (abs(number) >= 0.1 && number < 10) {
    dec <- 2
  } else if (abs(number) >= 0.001 && number < 0.1) {
    dec <- 3
  } else if (abs(number) < 0.001 && number != 0) {
    dec <- stringr::str_locate(format(
      abs(number), scientific = FALSE), "[1-9]{1}")[1] - 2
  } else if (number == 0) {
    dec <- 0
  }
  # Round number to decimal
  out <- format(round(number, dec), nsmall = dec, scientific = FALSE)
  
  # Replace Inf with infinte sign
  out <- gsub("Inf", "∞", out)

  # Remove leading zero if required
  if (out < 1 && lead_zero == FALSE) {
  out <- sub("0.", ".", out)
  }
  return(out)
}
report_desc <- function(descriptives, line) {
  ## ---------------------------
  ## Report descriptive statistics
  ##
  ## Takes a data.frame containing descriptive
  ## results and outputs a manuscript-ready string
  ## containing the mean and standard deviation
  ## e.g., "(M = 4.45, SD = 1.29)"
  ##
  ## @descriptives -- data.frame with
  ##        descriptive data
  ## @line -- line of descriptives data
  ##        to report
  ##
  ## @out string containing M and SD
  ## ---------------------------
  out <- paste0(
    "(*M* = ",
    forma(descriptives$mean[line]),
    ", *SD* = ",
    forma(descriptives$sd[line]),
    ")")
  return(out)
}
ci_pvaf <- function(F, DFn, DFd, N, conf.level = 0.9) {
  ## ---------------------------
  ## Report confidence intervals for ANOVA
  ##
  ## Wrapper for ci.pvaf that returns CIs in the format
  ## "[.002, .069]"
  ##
  ## @F -- F-value
  ## @DFn -- df numerator
  ## @DFd -- df denominator
  ## @N -- Total sample size
  ## @conf.level -- confidence level (default 90%)
  ##
  ## @return returns string of the format "[.002, .069]"
  ## ---------------------------
  ci <- unlist(MBESS::ci.pvaf(F, DFn, DFd, N, conf.level)[c(1, 3)])
  ci[is.na(ci)] <- 0
  ci_clean <- paste(lapply(ci, forma, 3, FALSE), collapse = ", ")
  ci_brackets <- paste0("[", ci_clean, "]")
  return(ci_brackets)
}
report_anova_result <- function(model, effect, one_sided = FALSE) {
  ## ---------------------------
  ## Report effect from ANOVA output
  ##
  ## Prints test statistics including
  ## partial eta squared and CI
  ##
  ## @model -- preprocessed ANOVA model
  ## @effect -- name of variable
  ##
  ## ---------------------------
  if((is.character(effect) & effect %in% model$Effect) |
      (is.numeric(effect) & effect %in% seq(1, length(model$Effect)))) {
    if(is.character(effect)) {
      mi <- model[model$Effect == effect, ]
    } else if(is.numeric(effect)) {
      mi <- model[effect, ]
    } else {
      stop("Error: The parameter effect has to be numeric or character.")
    }
    if(one_sided) {
      names(mi)[8] <- paste0((as.numeric(str_extract(names(mi)[8], "\\d{2}")) + 100) / 2, "% CI")
      mi[8] <- paste0("[", str_extract_all(pull(mi[8]), "\\.\\d{3}")[[1]][1], ", ∞]")
    }
    report <- paste0("*F*(", mi$DFn, ", ", mi$DFd, ") = ", mi$F, ", ", formp(mi$p),
      ", *$\\eta_p^2$* = ", mi$pes, ", ", names(mi)[8], " ", pull(mi[8]), sep = "")
  } else {
    # If effect does not exist print error message
    stop("Error: The specified effect does not exist.")
  }
  return(report)
}
report_t_test <- function(data, formula, paired = FALSE, alternative = "two.sided", ref_group = NA, conf_level = .95, one_sided_ci = FALSE) {
  ## ---------------------------
  ## Report t-test
  ##
  ## Prints test statistics including
  ## partial cohen's d(z) and CI
  ##
  ## @test -- t_test object
  ## @es -- cohens_d object
  ##
  ## ---------------------------
  
  # Run test
  test <- t_test(data, formula, paired = paired, alternative = alternative, ref.group = ref_group) 
  es <- cohens_d(data, formula, paired = paired, ci = TRUE, conf.level = conf_level, ref.group = ref_group)
  
  # If one-sided, increase confidence level and set more extreme bound to ∞
  if(alternative != "two.sided" & one_sided_ci) {
    conf_level <- (1 + conf_level) / 2
    conf_inf <- names(which.max(abs(es[c("conf.low", "conf.high")])))
    es[conf_inf] <- ifelse(es[conf_inf] > 0, Inf, -Inf)
  }

  # Print results
  d_print <- ifelse(paired == FALSE, ", *d* = ", ", *d~z~* = ")
  report <- paste("*t*(", ifelse(test$df%%1 == 0, test$df, forma(test$df, 2)), ") = ",
    forma(test$statistic), ", ", formp(test$p, text = TRUE), d_print, forma(es$effsize),
    ", ", conf_level * 100, "% CI [", forma(es$conf.low), ", ", forma(es$conf.high), "]", sep = "")
  return(report)
}
theme_cs_talk <- function(font = "Nunito", lab_size = 16, label_size = 14,
  dark = "#465263", light = "#E1E9ED", solid_facet = TRUE) {
  if (solid_facet) {
  facet_fill <- dark
  facet_text <- light
  } else if (!solid_facet) {
  facet_fill <- "transparent"
  facet_text <- dark
  }
  theme_bw(base_size = 16) %+replace%
  theme(
  # Rectangle elements
  plot.background = element_rect(fill = "transparent",
    color = NA_character_),
  panel.background = element_rect(fill = "transparent"),
  legend.background = element_rect(fill = "transparent", color = NA),
  strip.background = element_rect(color = facet_fill,
    fill = facet_fill, linewidth = 1),
  # Text elements
  plot.title = element_text(family = font, size = lab_size,
    face = "bold", hjust = 0, vjust = 2, color = dark),
  plot.subtitle = element_text(family = font,
    size = lab_size - 2, color = dark),
  plot.caption = element_text(family = font, size = lab_size,
    hjust = 1, color = dark),
  axis.title = element_text(family = font, size = lab_size,
    color = dark),
  axis.text = element_text(family = font, size = label_size,
    color = dark),
  axis.text.x = element_text(margin = margin(5, b = 10),
    color = dark),
  legend.title = element_text(family = font, size = lab_size,
    color = dark, hjust = 0),
  legend.text = element_text(family = font, size = label_size,
    color = dark),
  strip.text = element_text(family = font, size = label_size,
    color = facet_text, margin = margin(4, 4, 4, 4)),
  # Line elements
  axis.ticks = element_line(color = dark, linewidth = 0.5),
  legend.key = element_rect(fill = "transparent", color = NA_character_),
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.border = element_rect(color = dark, fill = NA, linewidth = 1)
  )
}
```

### Sample Characteristics
We collected data from a total of *N* = 389 participants using a Prolific representative sample that was stratified on the basis of age, sex, ethnicity, and political affiliation. Following our exclusion criteria we had to exclude 28 participants who inferred the wrong category in five or more non-target categorization items and one participant who rated their own data to be unfit for analysis. This resulted in *N* = 360 valid datasets (175 men, 180 women, 4 non-binary, 1 n/a; median age *Mdn* = `r round(median(dems$age, na.rm = TRUE), 1)` years, ranging from `r min(dems$age, na.rm = TRUE)` to `r max(dems$age, na.rm = TRUE)`). 42% of participants identified as Democrats, 23% as Independents, 33% as Republicans, and 2% as other. According to Prolific demographics, more participants identified as Independents (31% Democrats, 42% Independents, 27% Republicans)–possibly because there was no "Independent" option in our survey. Participants received monetary compensation of 1.20 GBP for completing the 8-minute study. Participants' mean political ideology was *M* = `r round(mean(dems$political_ideology, na.rm = TRUE), 1)` (*SD* = `r round(sd(dems$political_ideology, na.rm = TRUE), 1)`), on a scale from 0 = conservative to 100 = liberal. 80 additional people started the experiment on prolific but returned their submission, timed-out, did not meet the inclusion criteria, or failed the comprehension check.

### Exclusion of Statistical Outliers
We did not preregister exclusion of statistical outliers. However, upon inspection of the data we noticed that there were many data points that were very unlikely to reflect valid categorizations. That is, some participants in both the stereotype-disconfirming and the stereotype-confirming condition seemed to infer categories from opinions that are stereotypically associated with the opposing category (e.g., inferring from a pro-gun control opinion that the person must be a Republican). We assume that such responses are likely due to the participants understanding the items the wrong way around or responding at random. To investigate the potential effect of these outliers we conducted additional analyses excluding them. Theoretically, any values below the scale midpoint (50) are very unlikely to reflect genuine categorizations, because they would indicate that the category that is not stereotypically associated with the opinion is more likely to express the opinion than the category that is stereotypically associated with it. While it would therefore seem appropriate to exclude any values below 50, we decided to exclude values below 40, to account for the fact that participants may respond somewhat inaccurately using the sliding scale. For the main analyses we report tests with and without this exclusion criterion.

A similar problem occurred for the stereotype measure on which some participants indicated that category members would on average strongly disagree with opinions that are stereotypical for their category. However, for this measure there is less of a clear cutoff, because even an opinion that is very stereotypical or diagnostic for a category must not be shared by a majority of its members (as long as it is shared by considerably less members of the opposing category). To nevertheless investigate the effect of these outliers we conducted a multiverse analysis using several different cutoff criteria.

### Manipulation Check
#### Stereotype Measure {.tabset}
```{r stereotype ~ typicality * category_type, warning = FALSE, message = FALSE}
# Stereotype data
stereo_dat <- dat %>%
  filter(item_type == "target") %>%
  filter(diagnosticity_component == "COUNTERPROB")
```

##### Multiverse Outlier Correction
```{r stereotype ~ typicality * category_type multiverse, warning = FALSE, message = FALSE}
# Loop over all combinations of cutoffs and transformations
mv_stereo <- data.frame(
  cutoff = c("none", "fixed 1", "fixed 10", "fixed 20", "fixed 30", "fixed 40"),
  cutoff_value = c(0, 1, 10, 20, 30, 40))
for (c in seq_len(nrow(mv_stereo))) {
  mv_dat <- stereo_dat %>%
    filter(stereo >= mv_stereo$cutoff_value[c])

  # Run ANOVA
  mv_mod <- mv_dat %>%
    anova_test(dv = stereo,
      effect.size = "pes",
      between = c(category_type, typicality)) %>%
    as_tibble() %>%
    rowwise() %>%
    mutate(`90% CI` = ci_pvaf(F, DFn, DFd, nrow(mv_dat), 0.9),
      F = forma(`F`, 2), p = formp(p), pes = forma(pes, 3, FALSE))

  # Save test statistics
  mv_stereo$`n excluded`[c] <- nrow(stereo_dat) - nrow(mv_dat)
  mv_stereo$DFn[c] <- mv_mod$DFn[1]
  mv_stereo$DFd[c] <- mv_mod$DFd[1]
  mv_stereo$ct_F[c] <- mv_mod$F[1]
  mv_stereo$ct_p[c] <- mv_mod$p[1]
  mv_stereo$ct_pes[c] <- paste(mv_mod$pes[1], mv_mod[1, 8])
  mv_stereo$typ_F[c] <- mv_mod$F[2]
  mv_stereo$typ_p[c] <- mv_mod$p[2]
  mv_stereo$typ_pes[c] <- paste(mv_mod$pes[2], mv_mod[2, 8])
  mv_stereo$int_F[c] <- mv_mod$F[3]
  mv_stereo$int_p[c] <- mv_mod$p[3]
  mv_stereo$int_pes[c] <- paste(mv_mod$pes[3], mv_mod[3, 8])
}
# Print multiverse table
knitr::kable(select(mv_stereo, - cutoff_value),
  format = "markdown")
```

To test whether the manipulation was successful, we conducted a multiverse analysis with multiple fixed outlier cutoffs. We excluded participants with values below 1, 10, 20, 30, or 40 and conducted a two-way between-subjects ANOVA with the stereotype measure as the dependent variable and typicality and category type as between-subjects factors. The effect of typicality was marginally significant with no outlier exclusion and significant with all different outlier thresholds. The effect of category type and the two-way interaction were not significant in any of the tests. These results provide moderate support for the effectiveness of our manipulation.

##### Outlier Detection
```{r stereotype ~ typicality * category_type outlier, warning = FALSE, message = FALSE}
stereo_dat %>%
  ggplot(., aes(typicality, stereo, color = category_type)) +
  geom_boxplot(outlier.shape = NA) +
  geom_point(position = position_jitterdodge()) +
  labs(x = "Typicality", y = "Stereotype", color = "Category Type") +
  scale_color_manual(values = c("#849AB9", "#465263")) +
  theme_cs_talk()
```

##### QQ-Plot
```{r stereotype ~ typicality * category_type qq, message = FALSE}
stereo_dat %>%
  ggplot(., aes(sample = stereo)) +
  labs(x = "Theoretical quantiles", y = "Data quantiles") +
  stat_qq(color = "#000000") +
  stat_qq_line(color = "#000000") +
  facet_grid(category_type ~ typicality, labeller = "label_value") +
  theme_cs_talk()
```

### Party Categorization
#### Counterstereotype Probability {.tabset}
```{r categorization party ~ typicality, warning = FALSE, message = FALSE}
# Categorization data
inf_dat <- dat %>%
  filter(diagnosticity_component == "COUNTERPROB") %>%
  filter(category_type == "PARTY") %>%
  filter(item_type == "target")

# PREREGISTERED --  WITHOUT OUTLIER EXCLUSION
# Descriptives
inf_desc <- inf_dat %>%
  group_by(typicality) %>%
  get_summary_stats(inf, type = "mean_sd") %>%
  mutate(
    ci95_low = mean - 1.96 * sd / sqrt(n),
    ci95_upp = mean + 1.96 * sd / sqrt(n))

# Independent samples t-test
inf_report <- report_t_test(inf_dat, inf ~ typicality, paired = FALSE,
  alternative = "less", ref_group = "DIS", conf_level = .9, one_sided_ci = FALSE)

# WITH OUTLIER EXCLUSION
# Exclude outliers
inf_dat_ex <- inf_dat %>%
  filter(inf >= 40)

# Descriptives
inf_ex_desc <- inf_dat_ex %>%
  group_by(typicality) %>%
  get_summary_stats(inf, type = "mean_sd") %>%
  mutate(
    ci95_low = mean - 1.96 * sd / sqrt(n),
    ci95_upp = mean + 1.96 * sd / sqrt(n))

# Independent samples t-test
inf_ex_report <- report_t_test(inf_dat_ex, inf ~ typicality, paired = FALSE, 
  alternative = "less", ref_group = "DIS", conf_level = .9, one_sided_ci = FALSE)
```

For all of our analyses, we conducted one-sided independent samples *t* tests comparing political categorization in the stereotype-confirming and stereotype-disconfirming conditions. The tests for the counterstereotype probability condition were preregistered whereas the tests in the stereotype probability condition were exploratory. In the counterstereotype probability condition, the categorization into party categories was not significantly weaker when the stereotypes were disconfirmed `r report_desc(inf_desc, 1)` as opposed to when they were confirmed `r report_desc(inf_desc, 2)`, `r inf_report`.

After excluding `r sum(inf_desc$n) - sum(inf_ex_desc$n)` participants with outlying values, political categorization was significantly weaker when the stereotypes were disconfirmed `r report_desc(inf_ex_desc, 1)` as opposed to when they were confirmed `r report_desc(inf_ex_desc, 2)`, `r inf_ex_report`.

##### Descriptives
```{r categorization party ~ time * typicality descriptives}
knitr::kable(inf_desc, format = "markdown")
```

##### Outlier Detection
```{r categorization party ~ typicality outlier, warning = FALSE, message = FALSE, fig.width = 4}
inf_dat %>%
  ggplot(., aes(typicality, inf)) +
  geom_boxplot(outlier.shape = NA, color = "#465263") +
  geom_jitter(width = 0.2, color = "#465263") +
  labs(x = "Typicality", y = "Categorization") +
  theme_cs_talk()
```

##### QQ-Plot
```{r categorization party ~ typicality qq, message = FALSE}
inf_dat_ex %>%
  ggplot(., aes(sample = inf)) +
  labs(x = "Theoretical quantiles", y = "Data quantiles") +
  stat_qq(color = "#000000") +
  stat_qq_line(color = "#000000") +
  facet_grid(~ typicality, labeller = "label_value") +
  theme_cs_talk()
```

##### Moderation by partisan fit
```{r categorization party ~ typicality * partisan fit}
# Prepare data
inf_par_fit_dat <- inf_dat_ex %>%
  # Select participants who identify with one of the major parties
  filter(partisan_identity %in% c("Republican", "Democrat")) %>%
  # Recode partisan identity
  mutate(partisan_identity = case_match(partisan_identity,
    "Democrat" ~ "DEM", "Republican" ~ "REP")) %>%
  mutate(partisan_fit = as.factor(ifelse(
    partisan_identity == target_category_label,
    "same", "different")))

# Descriptives
inf_par_fit_desc <- inf_par_fit_dat %>%
  group_by(partisan_fit, typicality) %>%
  get_summary_stats(inf, type = "mean_sd") %>%
  mutate(
    ci95_low = mean - 1.96 * sd / sqrt(n),
    ci95_upp = mean + 1.96 * sd / sqrt(n))

# Run ANOVA
inf_par_fit_mod <- inf_par_fit_dat %>%
  anova_test(dv = inf,
    effect.size = "pes",
    between = c(partisan_fit, typicality)) %>%
  as_tibble() %>%
  rowwise() %>%
  mutate(`90% CI` = ci_pvaf(F, DFn, DFd, nrow(inf_par_fit_dat), 0.9),
    F = forma(`F`, 2), p = formp(p), pes = forma(pes, 3, FALSE))

knitr::kable(inf_par_fit_mod, format = "markdown")
```

It may be possible that the effect of diagnosticity on political categorization depends on the fit between the participant's party identification and the target's partisanship. We therefore ran an exploratory analysis examining the role of ideological fit (i.e., whether participant and target belong to the same category or a different one). We excluded participants classified as Independents and conducted a two-way between-subjects ANOVA with political categorization as the dependent variable and ideological fit and typicality as between-subjects factors. We found a significant effect of typicality. All other effects were non-significant.

##### Moderation by political issue
```{r categorization party ~ typicality * issue}
# Descriptives
inf_issue_desc <- inf_dat_ex %>%
  group_by(issue, typicality) %>%
  get_summary_stats(inf, type = "mean_sd") %>%
  mutate(
    ci95_low = mean - 1.96 * sd / sqrt(n),
    ci95_upp = mean + 1.96 * sd / sqrt(n))

# Run ANOVA
inf_issue_mod <- inf_dat_ex %>%
  anova_test(dv = inf,
    effect.size = "pes",
    between = c(issue, typicality)) %>%
  as_tibble() %>%
  rowwise() %>%
  mutate(`90% CI` = ci_pvaf(F, DFn, DFd, nrow(inf_dat_ex), 0.9),
    F = forma(`F`, 2), p = formp(p), pes = forma(pes, 3, FALSE))

knitr::kable(inf_issue_mod, format = "markdown")
```

We ran another exploratory analysis to test whether the effect of diagnosticity on political categorization was moderated by the issue for which diagnosticity was manipulated. We conducted a two-way between-subjects ANOVA with political categorization as the dependent variable and issue and typicality as between-subjects factors. We found a significant effect of typicality. All other effects were non-significant.

#### Stereotype Probability {.tabset}
```{r categorization party stereoprob ~ typicality, warning = FALSE, message = FALSE}
# Categorization data
inf_stereoprob_dat <- dat %>%
  filter(diagnosticity_component == "STEREOPROB") %>%
  filter(category_type == "PARTY") %>%
  filter(item_type == "target")

# WITHOUT OUTLIER EXCLUSION
# Descriptives
inf_stereoprob_desc <- inf_stereoprob_dat %>%
  group_by(typicality) %>%
  get_summary_stats(inf, type = "mean_sd") %>%
  mutate(
    ci95_low = mean - 1.96 * sd / sqrt(n),
    ci95_upp = mean + 1.96 * sd / sqrt(n))

# Independent samples t-test
inf_stereoprob_report <- report_t_test(inf_stereoprob_dat, inf ~ typicality, paired = FALSE,
  alternative = "less", ref_group = "DIS", conf_level = .9, one_sided_ci = FALSE)

# WITH OUTLIER EXCLUSION
# Exclude outliers
inf_stereoprob_dat_ex <- inf_stereoprob_dat %>%
  filter(inf >= 40)

# Descriptives
inf_stereoprob_ex_desc <- inf_stereoprob_dat_ex %>%
  group_by(typicality) %>%
  get_summary_stats(inf, type = "mean_sd") %>%
  mutate(
    ci95_low = mean - 1.96 * sd / sqrt(n),
    ci95_upp = mean + 1.96 * sd / sqrt(n))

# Independent samples t-test
inf_stereoprob_ex_report <- report_t_test(inf_stereoprob_dat_ex, inf ~ typicality, paired = FALSE,
  alternative = "less", ref_group = "DIS", conf_level = .9, one_sided_ci = FALSE)
```

In the stereotype probability condition, the categorization into party categories was not significantly weaker when the stereotypes were disconfirmed `r report_desc(inf_stereoprob_desc, 1)` as opposed to when they were confirmed `r report_desc(inf_stereoprob_desc, 2)`, `r inf_stereoprob_report`.

After excluding `r sum(inf_stereoprob_desc$n) - sum(inf_stereoprob_ex_desc$n)` participants with outlying values, political categorization was still not significantly weaker when the stereotypes were disconfirmed `r report_desc(inf_stereoprob_ex_desc, 1)` as opposed to when they were confirmed `r report_desc(inf_stereoprob_ex_desc, 2)`, `r inf_stereoprob_ex_report`.

##### Descriptives
```{r categorization party stereoprob ~ typicality descriptives}
knitr::kable(inf_stereoprob_desc, format = "markdown")
```

##### Outlier Detection
```{r categorization party stereoprob ~ typicality outlier, warning = FALSE, message = FALSE, fig.width = 4}
inf_stereoprob_dat %>%
  ggplot(., aes(typicality, inf)) +
  geom_boxplot(outlier.shape = NA, color = "#465263") +
  geom_jitter(width = 0.2, color = "#465263") +
  labs(x = "Typicality", y = "Categorization") +
  theme_cs_talk()
```

##### QQ-Plot
```{r categorization party stereoprob ~ typicality qq, message = FALSE}
inf_stereoprob_dat %>%
  ggplot(., aes(sample = inf)) +
  labs(x = "Theoretical quantiles", y = "Data quantiles") +
  stat_qq(color = "#000000") +
  stat_qq_line(color = "#000000") +
  facet_grid(~ typicality, labeller = "label_value") +
  theme_cs_talk()
```

### Ideological Categorization
#### Counterstereotype Probability {.tabset}
```{r categorization ideological ~ typicality, warning = FALSE, message = FALSE}
# Categorization data
inf_ideo_dat <- dat %>%
  filter(diagnosticity_component == "COUNTERPROB") %>%
  filter(category_type == "IDEOLOGICAL") %>%
  filter(item_type == "target")

# PREREGISTERED --  WITHOUT OUTLIER EXCLUSION
# Descriptives
inf_ideo_desc <- inf_ideo_dat %>%
  group_by(typicality) %>%
  get_summary_stats(inf, type = "mean_sd") %>%
  mutate(
    ci95_low = mean - 1.96 * sd / sqrt(n),
    ci95_upp = mean + 1.96 * sd / sqrt(n))

# Independent samples t-test
inf_ideo_report <- report_t_test(inf_ideo_dat, inf ~ typicality, paired = FALSE,
  alternative = "less", ref_group = "DIS", conf_level = .9, one_sided_ci = FALSE)

# WITH OUTLIER EXCLUSION
# Exclude outliers
inf_ideo_dat_ex <- inf_ideo_dat %>%
  filter(inf >= 40)

# Descriptives
inf_ideo_ex_desc <- inf_ideo_dat_ex %>%
  group_by(typicality) %>%
  get_summary_stats(inf, type = "mean_sd") %>%
  mutate(
    ci95_low = mean - 1.96 * sd / sqrt(n),
    ci95_upp = mean + 1.96 * sd / sqrt(n))

# Independent samples t-test
inf_ideo_ex_report <- report_t_test(inf_ideo_dat_ex, inf ~ typicality, paired = FALSE,
  alternative = "less", ref_group = "DIS", conf_level = .9, one_sided_ci = FALSE)
```

In the counterstereotype probability condition, the categorization into ideological categories was not significantly weaker when the stereotypes were disconfirmed `r report_desc(inf_ideo_desc, 1)` as opposed to when they were confirmed `r report_desc(inf_ideo_desc, 2)`, `r inf_ideo_report`.

After excluding `r sum(inf_ideo_desc$n) - sum(inf_ideo_ex_desc$n)` participants with outlying values, political categorization was significantly weaker when the stereotypes were disconfirmed `r report_desc(inf_ideo_ex_desc, 1)` as opposed to when they were confirmed `r report_desc(inf_ideo_ex_desc, 2)`, `r inf_ideo_ex_report`.

##### Descriptives
```{r categorization ideological ~ time * typicality descriptives}
knitr::kable(inf_ideo_desc, format = "markdown")
```

##### Outlier Detection
```{r categorization ideological ~ typicality outlier, warning = FALSE, message = FALSE, fig.width = 4}
inf_ideo_dat %>%
  ggplot(., aes(typicality, inf)) +
  geom_boxplot(outlier.shape = NA, color = "#465263") +
  geom_jitter(width = 0.2, color = "#465263") +
  labs(x = "Typicality", y = "Categorization") +
  theme_cs_talk()
```

##### QQ-Plot
```{r categorization ideological ~ typicality qq, message = FALSE}
inf_ideo_dat_ex %>%
  ggplot(., aes(sample = inf)) +
  labs(x = "Theoretical quantiles", y = "Data quantiles") +
  stat_qq(color = "#000000") +
  stat_qq_line(color = "#000000") +
  facet_grid(~ typicality, labeller = "label_value") +
  theme_cs_talk()
```

##### Moderation by ideological fit
```{r categorization ideological ~ typicality * ideological fit}
# Prepare data
inf_ideo_fit_dat <- inf_ideo_dat_ex %>%
  # Classify participants into ideological categories
  mutate(ideo_cat = case_when(
    political_ideology < 35 ~ "CON",
    political_ideology > 65 ~ "LIB",
    .default = "MOD")) %>%
  # Select participants who identify as liberal or conservative
  filter(ideo_cat %in% c("CON", "LIB")) %>%
  # Create ideological fit variable
  mutate(ideo_fit = as.factor(ifelse(
    ideo_cat == target_category_label,
    "same", "different")))

# Descriptives
inf_ideo_fit_desc <- inf_ideo_fit_dat %>%
  group_by(ideo_fit, typicality) %>%
  get_summary_stats(inf, type = "mean_sd") %>%
  mutate(
    ci95_low = mean - 1.96 * sd / sqrt(n),
    ci95_upp = mean + 1.96 * sd / sqrt(n))

# Run ANOVA
inf_ideo_fit_mod <- inf_ideo_fit_dat %>%
  anova_test(dv = inf,
    effect.size = "pes",
    between = c(ideo_fit, typicality)) %>%
  as_tibble() %>%
  rowwise() %>%
  mutate(`90% CI` = ci_pvaf(F, DFn, DFd, nrow(inf_ideo_fit_dat), 0.9),
    F = forma(`F`, 2), p = formp(p), pes = forma(pes, 3, FALSE))

knitr::kable(inf_ideo_fit_mod, format = "markdown")
```

It may be possible that the effect of diagnosticity on political categorization depends on the fit between the participant's ideological category and the target's category. We therefore ran an exploratory analysis examining the role of ideological fit (i.e., whether participant and target belong to the same category or a different one). We excluded participants classified as moderates and conducted a two-way between-subjects ANOVA with political categorization as the dependent variable and ideological fit and typicality as between-subjects factors. None of the effects were significant.

##### Moderation by political issue
```{r categorization ideological ~ typicality * issue}
# Descriptives
inf_ideo_issue_desc <- inf_ideo_dat_ex %>%
  group_by(issue, typicality) %>%
  get_summary_stats(inf, type = "mean_sd") %>%
  mutate(
    ci95_low = mean - 1.96 * sd / sqrt(n),
    ci95_upp = mean + 1.96 * sd / sqrt(n))

# Run ANOVA
inf_ideo_issue_mod <- inf_ideo_dat_ex %>%
  anova_test(dv = inf,
    effect.size = "pes",
    between = c(issue, typicality)) %>%
  as_tibble() %>%
  rowwise() %>%
  mutate(`90% CI` = ci_pvaf(F, DFn, DFd, nrow(inf_ideo_dat_ex), 0.9),
    F = forma(`F`, 2), p = formp(p), pes = forma(pes, 3, FALSE))

knitr::kable(inf_ideo_issue_mod, format = "markdown")
```

We ran another exploratory analysis to test whether the effect of diagnosticity on political categorization was moderated by the issue for which diagnosticity was manipulated. We conducted a two-way between-subjects ANOVA with political categorization as the dependent variable and issue and typicality as between-subjects factors. We found a significant effect of issue that was likely driven by weaker categorization in the affirmative action condition. Moreover, we found a significant effect of typicality. The interaction was not significant.

#### Stereotype Probability {.tabset}
```{r categorization ideological stereoprob ~ typicality, warning = FALSE, message = FALSE}
# Categorization data
inf_stereoprob_ideo_dat <- dat %>%
  filter(diagnosticity_component == "STEREOPROB") %>%
  filter(category_type == "IDEOLOGICAL") %>%
  filter(item_type == "target")

# WITHOUT OUTLIER EXCLUSION
# Descriptives
inf_stereoprob_ideo_desc <- inf_stereoprob_ideo_dat %>%
  group_by(typicality) %>%
  get_summary_stats(inf, type = "mean_sd") %>%
  mutate(
    ci95_low = mean - 1.96 * sd / sqrt(n),
    ci95_upp = mean + 1.96 * sd / sqrt(n))

# Independent samples t-test
inf_stereoprob_ideo_report <- report_t_test(inf_stereoprob_ideo_dat, inf ~ typicality, paired = FALSE,
  alternative = "less", ref_group = "DIS", conf_level = .9, one_sided_ci = FALSE)

# WITH OUTLIER EXCLUSION
# Exclude outliers
inf_stereoprob_ideo_dat_ex <- inf_stereoprob_ideo_dat %>%
  filter(inf >= 40)

# Descriptives
inf_stereoprob_ideo_ex_desc <- inf_stereoprob_ideo_dat_ex %>%
  group_by(typicality) %>%
  get_summary_stats(inf, type = "mean_sd") %>%
  mutate(
    ci95_low = mean - 1.96 * sd / sqrt(n),
    ci95_upp = mean + 1.96 * sd / sqrt(n))

# Independent samples t-test
inf_stereoprob_ideo_ex_report <- report_t_test(inf_stereoprob_ideo_dat_ex, inf ~ typicality, paired = FALSE,
  alternative = "less", ref_group = "DIS", conf_level = .9, one_sided_ci = FALSE)
```

In the stereotype probability condition, the categorization into ideological categories was not significantly weaker when the stereotypes were disconfirmed `r report_desc(inf_stereoprob_ideo_desc, 1)` as opposed to when they were confirmed `r report_desc(inf_stereoprob_ideo_desc, 2)`, `r inf_stereoprob_ideo_report`.

After excluding `r sum(inf_stereoprob_ideo_desc$n) - sum(inf_stereoprob_ideo_ex_desc$n)` participants with outlying values, political categorization was still not significantly weaker when the stereotypes were disconfirmed `r report_desc(inf_stereoprob_ideo_ex_desc, 1)` as opposed to when they were confirmed `r report_desc(inf_stereoprob_ideo_ex_desc, 2)`, `r inf_stereoprob_ideo_ex_report`.

##### Descriptives
```{r categorization ideological stereoprob ~ typicality descriptives}
knitr::kable(inf_stereoprob_ideo_desc, format = "markdown")
```

##### Outlier Detection
```{r categorization ideological stereoprob ~ typicality outlier, warning = FALSE, message = FALSE, fig.width = 4}
inf_stereoprob_ideo_dat %>%
  ggplot(., aes(typicality, inf)) +
  geom_boxplot(outlier.shape = NA, color = "#465263") +
  geom_jitter(width = 0.2, color = "#465263") +
  labs(x = "Typicality", y = "Categorization") +
  theme_cs_talk()
```

##### QQ-Plot
```{r categorization ideological stereoprob ~ typicality qq, message = FALSE}
inf_stereoprob_ideo_dat %>%
  ggplot(., aes(sample = inf)) +
  labs(x = "Theoretical quantiles", y = "Data quantiles") +
  stat_qq(color = "#000000") +
  stat_qq_line(color = "#000000") +
  facet_grid(~ typicality, labeller = "label_value") +
  theme_cs_talk()
```